\documentclass{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[linesnumbered]{algorithm2e}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{systeme}
\usepackage{enumitem}   


\title{SDSU \\ COMP521 Fall 2022}
\author{Homework 03 - Due Date: 09/30/2022}
\pagenumbering{gobble}


\begin{document}

\maketitle

\section*{Problem}
Calculate finite difference approximation of $u''(x)$ for the function $u(x) = x^2 - cos(10x)$ on the interval $x \in [0.4,1]$. You have to implement the following finite difference approximation:

\begin{equation*}
	\frac{-u_{i+2} + 16u_{i+1}-30u_i+16u_{i-1} - u_{i-2}}{12\Delta x^2}
\end{equation*}

You have to determine the order of accuracy of this approximation. Follow the instructions below.\\

\section*{Instructions}
\begin{enumerate}
	\item You have to work on your solution using the following MATLAB files:
	\begin{itemize}
		\item \textbf{main.m }
		\item \textbf{Fx.m}
		\item \textbf{secderivativeactual.m}
		\item \textbf{secderivativeapprox.m}
	\end{itemize}
    The MATLAB files have comments that will guide you. Read them carefully.
	\item Show the $loglog$ plots with the error metrics versus the grid sizes.
	\item Fit the $loglog$ plots to a straight line. Use the fit to determine the order of accuracy. Explain.
	\item Discuss the differences from using different metrics. Do they lead to the same conclusion about the order of accuracy?
\end{enumerate}


\textbf{Deliverable:} Submit a .PDF file with your report. Submit all the code files with your modifications.


\end{document}